Outdated and License-Violating Code on Stack Overflow

### 2017-05-02 cloneoverflow-latex/rebuttal/rebuttal.txt

REVIEWER 1

Question 1: 
This study is motivated by [1, 2]. An et al. [2] found that 62 active Android projects contains 232 exact copies of snippets on Stack Overflow (SO) with confirmation from the developers. 60 apps have license violations between the copied snippets and project's license. 126 snippets are found to potentially migrate from one app to another via SO posts, i.e. 'code laundering'. Acar et al. [1] found that SO is often chosen by programmers when solving tasks. They examined 139 SO threads used by the participants in four Android security-related tasks and found that only 17% of them contain secure snippets. The same security-related problems are discovered in a random sampling of 200,000 apps from Google Play (e.g. 98.9% implement insecure hostname verifier similarly to the SO examples).

Question 2:
The motivation still holds. It is known that clone detection tools report a lot of false/trivial clones. We focus on the important ones. The number of 32,533 analysed clone pairs are the ones that are not trivial clones according to the clone agreement and clone filtering process for feasibility of a manual study. However, they are not the 'total' number of clones between SO and Qualitas.

Question 3:
No. We cannot expect the same results from a different pair of evaluators. Classifications of clones by human are known to be very subjective. However, we expect similar results with a higher number of evaluators.

Question 4:
Although the code is provided as minimum working examples, it is known that the code is used as-is and causing problems in active projects [1,2]. Active maintenance and support provided by SO can mitigate such problems

REVIEWER 2

Question 1:
We are not aware of any curated set of software that includes non-open source projects. We focused on open source projects to allow replication of our study.

Question 2:
See Table 11: 79 (QS) and 77 (EX) pairs (snippets) violate the license but acknowledge the source, 202 (UD) pairs violate the license and have no acknowledgement.

REVIEWER 3

Question 1:
Disagreed clone pairs are also clones, they just have lower confidence to be true clones. By only inspecting agreed clones, one would miss several true clones due to the tools' differences [61].

Question 3:
We consider them as two clone pairs. From 32,533 online clone pair candidates, there are 4,018 distinct Qualitas clones (file + start + end lines) and, on average, each of them forms a clone pair with 7.6 distinct Stack Overflow snippets.

Question 4:
The automatic classification of boiler plate code is done first (Figure 2). The manual investigation (Figure 4) only classifies boiler plate clones that have been missed by the automatic classification. During the manual investigation, the classification of accidental clones is easier than the boiler plate classification, thus it comes second.

Question 5:
See Table 7: for the manual confirmed pairs, 516/144,064 of snippets with on average 26% of the snippets' code. And for the reported pairs, 14,856/144,064 with an average of 38%. Note that it is restricted to only 111 Qualitas projects and one can expect a large number of clones to other projects.

### 2017-08-13 cloverflow-tse/cloverflow.tex
Added TSE-formatted paper.

\documentclass[sigconf,review, anonymous]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
%\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage[normalem]{ulem}

@@

% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
%\acmYear{2017}
%\copyrightyear{2017}

%\acmPrice{15.00}

\overfullrule1ex

\begin{document}
	\title{Outdated and License-Violating Code on Stack Overflow}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke}
\affiliation{%
	\institution{CREST, University College London}
	%  \streetaddress{P.O. Box 1212}
	\city{London, UK} 
	%  \state{Ohio} 
	%  \postcode{43017-6221}
}
%\email{{ucabagk,matheus.paixao.14,j.krinke}@ucl.ac.uk}

\author{Giuseppe Bianco,~Rocco Oliveto}
\affiliation{%
	\institution{University of Molise}
	%  \streetaddress{P.O. Box 1212}
	\city{Pesche (IS), Italy} 
	%  \state{Ohio} 
	%  \postcode{43017-6221}
}

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter detected
  online clone pairs between 144,064 Java code snippets on Stack
  Overflow and 111 Java open source projects in the curated Qualitas
  corpus. We discovered and analysed 32,533 non-trivial online clone
  candidates. Our investigation of 3,636 manually confirmed clone
  pairs revealed strong evidence that 112 clones have been copied from
  a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
  to be outdated and potentially harmful for reuse.  Furthermore, we
  found 357 code snippets on Stack Overflow that violate the license
  of their original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10011007.10011006.10011072</concept_id>
	<concept_desc>Software and its engineering~Software libraries and repositories</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10011074.10011111.10011113</concept_id>
	<concept_desc>Software and its engineering~Software evolution</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Software libraries and repositories}
\ccsdesc[300]{Software and its engineering~Software evolution}

% We no longer use \terms command
%\terms{Theory}

\keywords{Clone Detection, Stack Overflow, Outdated Code, Software Licensing}

\maketitle

\section{Introduction}

@@

%\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.

@@

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{description}
\item[RQ1 (Online code clones):] \textit{To what extent is source
  code cloned between Stack Overflow and open source projects?} We
quantitatively measured the number of online code clones between Stack
Overflow and open source projects to understand the scale of the
problem. 
\item[RQ2 (Patterns of online code clones):] \textit{Why do online
  code clones occur?} We categorised online clones into seven
categories allowing insights to why online code clones are created.
\item[RQ3 (Outdated online code clones):] \textit{Are
  online code clones up-to-date compared to their counterparts in the
  original projects?} We were interested in the outdated Stack
Overflow code examples since users are potentially reusing
them. 
\item[RQ4 (Software licensing violation):] \textit{Do
  licensing conflicts occur between Stack Overflow clones and their
  originals?} We investigated whether the reuse of online code clones
can cause software developers to violate licenses.
\end{description}

@@

\begin{table}
  \centering
  \caption{Stack Overflow and Qualitas datasets}
  \label{tab:datasets}
  %\small
  \begin{tabular}{lrrr}
    \hline 
    Dataset & No. of files & SLOC & Median \\
    \hline
    Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
    %\hline 
    Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
    \hline 
  \end{tabular} 
\end{table}

@@

\textbf{Simian} is a text-based clone detector that locates clones at
line-level granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
  Krinke2010}.
% It is a command-line tool which enables us to automate the
% detection. 
Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones
(type-1) and parameterised clones (type-2). \textbf{NiCad} is also a
text-based clone detector which detects clones at either method- or
block-level granularity. It can detect clones of type-1, -2 up to
type-3 (clones with added and removed statements) and has
also been used in several empirical clone studies~\cite{Roy2008,
  Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
  Sajnani2016}. NiCad utilises TXL~\cite{Cordy2006} for parsing and
pretty-printing source code and provides code normalisation by
variable renaming and abstraction. We use a variant of NiCad called
\textit{nicadcross}. It offers the same functionalities as the
original NiCad but is specialised for detecting code clones between
two systems. 
% NiCad is also a command-line tool which makes it suitable for
% automation.

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the clone detection accuracy. Then, we
deployed the two detectors to locate clones between the two
datasets.  For each Qualitas project, we ran the tools on the
project's code and the entire Stack Overflow data.
% For scalability reasons, we partitioned the input and ran the tools
% multiple times. Each run was composed of the entire Stack Overflow
% data and a single Qualitas project. We repeated the process until we
% covered all 111 projects.
% We then converted the clone reports to the General
% Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
% single GCF file.  
Simian did not provide an option to detect cross-project
clones. % between two locations.
Hence the Simian clone report was filtered to contain only clone pairs
between Stack Overflow and Qualitas projects, removing all clone pairs
within either Stack Overflow or within Qualitas.
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.

\begin{table}
  \centering
  \caption{Configurations of Simian and NiCad}
  \label{t:param_tuning}
  %	\resizebox{\columnwidth}{!}{%
  \small
  \begin{tabular}{p{0.7cm}|p{2.4cm}p{3.8cm}}
    \hline 
    Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
    \hline
    Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\ 
    \hline 
    NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
    \hline
  \end{tabular} %
%}
\end{table}

@@

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\hline
		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
		\hline
		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
		\hline
	\end{tabular} %
	%}
\end{table}

@@

\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
  original study, we selected a threshold of 0.7 for
  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\textperthousand~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

\begin{table}
  \centering
  \caption{Distribution of the agreed clone pairs}
  \label{t_agreed_good_clone_pairs}
  %\small
  %	\resizebox{\columnwidth}{!}{%
  \begin{tabular}{l|r|r|r|r|r}
    \hline
    Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
    \hline
    \textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
    \textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
    \hline
  \end{tabular} %
  % }
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-4}
		& & \textit{L} & \textit{S} & \\ 
		\hline 
		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
		\hline
		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
	\end{tabular} %
	%}
\end{table}

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
        \small\vspace{-1ex}
		\begin{tabular}{c@{~~}p{7.35cm}}
			\hline 
			Patt. & Description \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\

@@

			AC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	%}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}\vspace{-1ex}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\subsection{Phase 5: Outdated Clones}
Outdated code occurs when a piece of code has been copied from its
origin to another location and later the original has been
updated~\cite{Xia2014}. Usually code clone detection is used to locate
clone instances and update them to match with the
originals~\cite{Bellon2007}. However, online code clones are more
difficult to detect than in regular software projects due to its large
search space and a mix of natural and programming languages combined
in the same post.
%Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.

To search for outdated online code clones, we focused on the
\textbf{QS} clone pairs that were cloned from Qualitas to Stack
Overflow and compared them with their latest versions. We downloaded
the latest version of the Qualitas projects from their repositories on
September 26, 2016. For each \textbf{QS} online clone pair, we used the
clone from Qualitas as a proxy. We searched for its latest version by
the file name and located the cloned region in the file based on the
method name.
%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
We then compared the Stack Overflow snippet to its latest version
line-by-line to find if any change has been made to the source
code. We also made sure that the changes did not come from the
modifications made to the Stack Overflow snippets by the posters but
from the updates in the projects themselves. When we found
inconsistent lines between the two versions, we used
{\small\texttt{git blame}} to see who modified those lines of code and
the timestamps.

\subsection{Phase 6: Licensing Analysis}
Software licensing plays an important role in software
development. Violation of software licenses impacts software delivery
and also leads to legal issues~\cite{Sprigman2015}.
%It is an emerging area that software engineering research community is paying attention to. For example, 
One can run into a licensing issue if one integrates third-party
source code into their software without checking. A study by An et
al.~\cite{An2017} reports 1,279 cases of potential license violations
between 399 Android apps and Stack Overflow code
snippets.

@@

% The table shows the license mapping of Stack Overflow snippets and
% Qualitas source code. The results are reported separately for the
% \textbf{QS}, \textbf{EX}, and \textbf{UD} set.

%\subsection{Analysis Methods}

% We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
% to answer our four research questions. 
% To answer RQ1, we rely on the number of manually validated true positive online clone pairs
% in phase 3. We use the results of the manual classification using the
% patterns of online code cloning to answer RQ2. 
% For RQ3, we looked at the true positive clone pairs that are classified 
% as cloned from Qualitas to Stack Overflow and
% checked if they have been changed since they have been
% cloned. Similarly, for RQ4, we looked at the license of each clone in the pattern 
% QS, EX, UD and checked for a possibility of a licensing violation.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

\usepackage{booktabs} % For formal tables
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
%\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amsfonts}

@@

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Outdated and License-Violating Code on Stack Overflow}

\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke,~Giuseppe Bianco,~Rocco Oliveto}

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers don't need this extra clearance.)

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
% We studied online code clones on the popular programming Q\&A
% website, Stack Overflow, and their issues on outdated code and
% software licensing violations. 
Online code clones are code fragments that are copied from software
projects or online sources to Stack Overflow as examples in
questions and answers.
% They can be discovered by using code clone
% detectors, yet they are inherently different from normal code clones
% in software projects in several aspects. 
Due to an absence of a checking mechanism after the code has been
copied to Stack Overflow, online code clones may suffer from
becoming outdated or violating the original software license.
% Moreover, we also found that majority of online code clones do not
% contain the license of their originals.
We present a study incorporating several state-of-the-art tools and
techniques to automatically extract, prioritise, and filter detected
online clone pairs between 144,064 Java code snippets on Stack
Overflow and 111 Java open source projects in the curated Qualitas
corpus. We discovered and analysed 32,533 non-trivial online clone
candidates. Our investigation of 3,636 manually confirmed clone
pairs revealed strong evidence that 112 clones have been copied from
a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
to be outdated and potentially harmful for reuse.  Furthermore, we
found 357 code snippets on Stack Overflow that violate the license
of their original software.
% These snippets are questionable for reuse.
% Our study is among the first to address the problem of
% outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Clone Detection, Stack Overflow, Outdated Code, Software Licensing
\end{IEEEkeywords}}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

@@

@@

We performed an empirical study of online code clones between Stack
Overflow and 111 Java open source projects to answer the following
research questions:
\begin{itemize}
	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
		code cloned between Stack Overflow and open source projects?} We
	quantitatively measured the number of online code clones between Stack
	Overflow and open source projects to understand the scale of the
	problem. 
	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
		code clones occur?} We categorised online clones into seven
	categories allowing insights to why online code clones are created.
	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
		online code clones up-to-date compared to their counterparts in the
		original projects?} We were interested in the outdated Stack
	Overflow code examples since users are potentially reusing
	them. 
	\item \textbf{RQ4 (Software licensing violation): }\textit{Do
		licensing conflicts occur between Stack Overflow clones and their
		originals?} We investigated whether the reuse of online code clones
	can cause software developers to violate licenses.
	\item \textbf{RQ5 (Developers' awareness): }\textit{Do Stack Overflow
		users aware of the outdated code and licensing problem when
		they answer a question on Stack Overflow?} 
	We surveyed 600 high reputation Stack Overflow users to study their
	awareness of the issues.
\end{itemize}

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	%\small
	\begin{tabular}{lrrr}
		\toprule
		Dataset & No. of files & SLOC & Median \\
		\midrule
		Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

@@

\textbf{Simian} is a text-based clone detector that locates clones at line-level
granularity and has been used extensively in several clone
studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
(strings and numbers) which enables Simian to detect literal clones (type-1) and
parameterised clones (type-2). \textbf{NiCad} is also a text-based clone
detector which detects clones at either method- or block-level granularity. It
can detect clones of type-1, -2 up to type-3 (clones with added and removed
statements) and has also been used in several empirical clone
studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
	Sajnani2016}. NiCad utilises TXL~\cite{Cordy2006} for parsing and
pretty-printing source code and provides code normalisation by variable renaming
and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers
the same functionalities as the original NiCad but is specialised for detecting
code clones between two systems.

We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the clone detection accuracy. Then, we deployed the
two detectors to locate clones between the two datasets.  For each Qualitas
project, we ran the tools on the project's code and the entire Stack Overflow
data. Simian did not provide an option to detect cross-project clones. Hence the
Simian clone report was filtered to contain only clone pairs between Stack
Overflow and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas.

\begin{table}
	\centering
	\caption{Configurations of Simian and NiCad}
	\label{t:param_tuning}
%		\resizebox{\columnwidth}{!}{
	\small
	\begin{tabular}{p{0.8cm}|p{2.5cm}p{3.8cm}}
		\toprule
		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
		\midrule
		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\ 
		\bottomrule
		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
		\hline
	\end{tabular} %
%	}
\end{table}

@@

\begin{table}
	\centering
	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:orig_stats}
	%\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r}
		\toprule
		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
		\midrule
		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
		\bottomrule
	\end{tabular} %
	%}
\end{table}

@@

\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
agreement filtering using Bellon's criteria\footnote{Similar to the
	original study, we selected a threshold of 0.7 for
	\textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
clone pairs is 32,316, 0.1\%~of all reported clone
pairs.  Agreed clone pairs are clone pairs that pass Bellon's
\textit{good} or \textit{ok} criteria, and therefore are selected for
manual classification.  Due to NiCad's failures, we do not have NiCad
clones from five Qualitas projects in the agreed clone pairs. Simian
clones of the same projects also disappeared from the agreed clone
pairs since they could not be matched.

\begin{table}
	\centering
	\caption{Distribution of the agreed clone pairs}
	\label{t_agreed_good_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r}
		\toprule
		Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
		\midrule
		\textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
		\textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
		\bottomrule
	\end{tabular} %
	% }
\end{table}

@@

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|r}
		\toprule
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cmidrule{3-4}
		& & \textit{L} & \textit{S} & \\ 
		\midrule 
		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
		\bottomrule
		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
	\end{tabular} %
	%}
\end{table}

@@

\begin{table}
	\centering
	\caption{The seven patterns of online code cloning}
	\label{tab:classification_scheme}
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{c@{~~}p{7.35cm}}
		\toprule
		Patt. & Description \\ 
		\midrule
		QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\

@@

		AC & Accidental similarity, false clones \\ 
		\bottomrule 
	\end{tabular}  %
	%}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{classification_process}\vspace{-1ex}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\subsection{Phase 5: Outdated Clones} Outdated code occurs when a piece of code
has been copied from its origin to another location and later the original has
been updated~\cite{Xia2014}. Usually code clone detection is used to locate
clone instances and update them to match with the originals~\cite{Bellon2007}.
However, online code clones are more difficult to detect than in regular
software projects due to its large search space and a mix of natural and
programming languages combined in the same post.

To search for outdated online code clones, we focused on the \textbf{QS} clone
pairs that were cloned from Qualitas to Stack Overflow and compared them with
their latest versions. We downloaded the latest version of the Qualitas projects
from their repositories on September 26, 2016. For each \textbf{QS} online clone
pair, we used the clone from Qualitas as a proxy. We searched for its latest
version by the file name and located the cloned region in the file based on the
method name. We then compared the Stack Overflow snippet to its latest version
line-by-line to find if any change has been made to the source code. We also
made sure that the changes did not come from the modifications made to the Stack
Overflow snippets by the posters but from the updates in the projects
themselves. When we found inconsistent lines between the two versions, we used
{\small\texttt{git blame}} to see who modified those lines of code and the
timestamps.

\subsection{Phase 6: Licensing Analysis} Software licensing plays an important
role in software development. Violation of software licenses impacts software
delivery and also leads to legal issues~\cite{Sprigman2015}. 
One can run into a licensing issue if one integrates third-party source code
into their software without checking. A study by An et al.~\cite{An2017} reports
1,279 cases of potential license violations between 399 Android apps and Stack
Overflow code snippets.

@@

\subsection{Stack Overflow Developers' Survey} We support our findings of
outdated and license-violating code snippets on Stack Overflow by asking Stack
Overflow users to take an online survey. The survey was used for assessing awareness of
the developers on the two issues of outdated code and licensing-violating code
snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
anonymous and the participants could decide to leave at any time. It contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our \FIXME{technical
	report/website?} ~\footnote{Stack Overflow Answerers' Survey:
	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.

\begin{table}
	\centering
	\caption{The two groups of Stack Overflow users invited to take the survey}
	\label{tab:survey_target}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Group 1 & 963,731--7,674 & 300 & 112 & 37\% \\
		Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
		\bottomrule
	\end{tabular}
\end{table}
